Abstract Binding Trees

### 2015-11-06 paper.tex
Fix script option passing behavior
Apparently options to the class are only globally inherited by loaded
packages if the options are written directly on the class line within
the document. If the options are specified with `\PassOptionsToClass`
they only affect the class itself so we need to also provide a
`\PassOptionsToPackage` for each individual package.
Use draft for more pkgs; don't run bibtex in draft
Fix some warnings
Fix some overfulls

\documentclass[draft,11pt]{article}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{agda} % this should come after ams*
\usepackage{catchfilebetweentags}
\usepackage{fontspec}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{ifthen}
\usepackage{mathtools}
\usepackage{proof}
\usepackage{scalerel}
\usepackage{setspace}
\usepackage{stmaryrd}
\usepackage{supertabular}
\usepackage{tikz-cd}
\usepackage{unicode-math}
\usepackage{url}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{xunicode}

@@

Then, the interpretation of a term in a model $P$ is a map from its environment
to $P$, that is,
$\Of{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash
M:s}_P}{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P\to P_s}$.
The interpretation of a variable
$\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash x_j:s}_P$
simply projects it of the environment and embeds it into the
model, as follows:
\[
  \begin{tikzcd}[ampersand replacement = \&]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}} \arrow[r, "\IMode{\pi_3}"]
    \& {\IMode{V^{[\Gamma]}}} \arrow[r, "\IMode{\nu_{\Gamma}}"]
    \& {\IMode{P^{[\Gamma]}}} \arrow[r, "\IMode{\pi_j}"]
    \& \IMode{P_s}
  \end{tikzcd}
  \tag{var}
\]

The interpretation of metavariable applications
$\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash
\MApp{\MV{m}_i}{u_0,\dots,u_m}{M_0,\dots,M_n} : s}_P$, where
$\Lookup{\Omega}{\MV{m}}{\MkValence{\vec{p}}{\vec{q}}{s}}$, proceeds by projecting the metavariable's interpretation from the environment and intantiating it via substitution:
\[
  \begin{tikzcd}[ampersand replacement = \&, sep=huge]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}}
          \arrow[r, "\IMode{\Tuple{\pi_i\,\pi_1, \phi\,\pi_2, \psi}}"]
    \& {\IMode{P_{s'}^{\Yoneda{\vec{p}\parallel\vec{q}}}\times S^{\{\vec{p}\}} \times P^{[\vec{q}]}}}
          \arrow[r, "\IMode{\varsigma_{\vec{p}\parallel\vec{q}}}"]
    \& \IMode{P_s}
  \end{tikzcd}
  \tag{metavar}
\]
where
\begin{align*}
  \ADefine{\phi}{
    \Dom{\vec{p}}\mapsto \vec{u}
  }\\
  \ADefine{\psi}{
    \Tuple{
      \SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash M_j:q_j}_P
    }_{j\leq n}
  }
\end{align*}

@@

\nocite{*}
\bibliographystyle{abbrv}
\bibliography{refs}

>>>>

\documentclass[11pt]{article}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{agda} % this should come after ams*
\usepackage{catchfilebetweentags}
\usepackage{fontspec}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{ifdraft}
\usepackage{ifthen}
%\usepackage{mathtools}
\usepackage{proof}
\usepackage{scalerel}
\usepackage{setspace}
\usepackage{stmaryrd}
\usepackage{supertabular}
\usepackage{tikz-cd}
\usepackage{unicode-math}
\usepackage{url}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{xunicode}

@@

Then, the interpretation of a term in a model $P$ is a map from its environment
to $P$:
\[%
  \Of{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash%
      M:s}_P}{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P\to P_s}%
\]%
The interpretation of a variable
$\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash x_j:s}_P$ simply
projects it of the environment and embeds it into the model, as follows:
\[
  \begin{tikzcd}[ampersand replacement = \&]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}} \arrow[r, "\IMode{\pi_3}"]
    \& {\IMode{V^{[\Gamma]}}} \arrow[r, "\IMode{\nu_{\Gamma}}"]
    \& {\IMode{P^{[\Gamma]}}} \arrow[r, "\IMode{\pi_j}"]
    \& \IMode{P_s}
  \end{tikzcd}
  \tag{var}
\]

Next we have the interpretation of metavariable applications
\[%
  \SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash%
    \MApp{\MV{m}_i}{u_0,\dots,u_m}{M_0,\dots,M_n} : s}_P%
  \qquad(\Lookup{\Omega}{\MV{m}}{\MkValence{\vec{p}}{\vec{q}}{s}})
\]
which proceeds by projecting the metavariable's interpretation from the
environment and intantiating it via substitution:
\[
  \begin{tikzcd}[ampersand replacement = \&, sep=huge]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}}
          \arrow[r, "\IMode{\Tuple{\pi_i\,\pi_1, \phi\,\pi_2, \psi}}"]
    \& {\IMode{P_{s'}^{\Yoneda{\vec{p}\parallel\vec{q}}}\times S^{\{\vec{p}\}} \times P^{[\vec{q}]}}}
          \arrow[r, "\IMode{\varsigma_{\vec{p}\parallel\vec{q}}}"]
    \& \IMode{P_s}
  \end{tikzcd}
  \tag{metavar}
\]
where
\begin{align*}
  \ADefine{\phi}{
    \Dom{\vec{p}}\mapsto \vec{u}
  }\\
  \ADefine{\psi}{
    \Tuple{
      \SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash M_j:q_j}_P
    }_{j\leq n}
  }
\end{align*}

@@

\ifdraft{}{
  \nocite{*}
  \bibliographystyle{abbrv}
  \bibliography{refs}
}
